---
title: "W241 Final Project"

output: 
    github_document: default
---

#Data Analysis Pipeline


```{r, results='hide'} 
# load packages 
library(data.table)
library(foreign)
library(miceadds)
library(sandwich)
library(magrittr)
library(dplyr)
library(lfe)
library(lmtest)                        
library(multiwayvcov)             
library(stargazer)  
library(ggplot2)
library(reshape2)
library(ri2)
library(randomizr)
library(estimatr)
library(PerformanceAnalytics)
library(lsr)
library(pwr)
```

## Initial Data Load

### Load the data
```{r}
d <- fread("/Users/brea/Downloads/ImpactDataViz.pilot_July_16.csv")
head(d)
```

### Extract the data from specific date
```{r}
d <- na.omit(d)
data_16 <- d  %>% filter(startsWith(StartDate, '7/16/20'))
data_16$FL_24_DO[data_16$FL_24_DO=='DataVisualization(Treatment)'] <- 1
data_16$FL_24_DO[data_16$FL_24_DO=='DataVisualization(Control)'] <- 0
data_16$Q9[data_16$Q9=='1'] <- 1
data_16$Q9[data_16$Q9=='2'] <- 0
data_16$Q10[data_16$Q10=='1'] <- 1
data_16$Q10[data_16$Q10=='2'] <- 0
data_16$Q11[data_16$Q11=='1'] <- 1
data_16$Q11[data_16$Q11=='2'] <- 0
data_16$Q18 <- as.numeric(data_16$Q18)
data_16$Q19 <- as.numeric(data_16$Q19)
```


## Random Inference

### Calculate ATE
```{r}
estimate_ate <- function(dt, outcome, treatment) { 
  ## This takes a data.table, the name of the outcome variable, and the name
  ## of the treatment indicator. 
  dt <- na.omit(dt)
  g <- dt[ , .(group_mean = mean(get(outcome))), keyby = .(get(treatment))]
  diff <- g[, diff(group_mean)]
  return(diff)
}
ate_18 <- estimate_ate(data_16, outcome = 'Q18', treatment = 'FL_24_DO')
ate_19 <- estimate_ate(data_16, outcome = 'Q19', treatment = 'FL_24_DO')
ate_18
```

### Random Inference

```{r}
set.seed(2)
assignment <- function(d) { 
  length <- dim(d)[1]
  sample(c(rep(0,length/2),rep(1,length/2)))
} 

make_data <- function(d) {
  dt <- (cbind(d, treatment_v2 = assignment(d)))
  return(dt)
}

ates <- function(simulations = 10000,d, oc) {
  res <- NA   
  for(sim in 1:simulations) { 
    dt <- make_data(d)
    res[sim] <- estimate_ate(dt, outcome = oc, treatment = 'treatment_v2')
  }
  return(res)
}
ate_result <- ates(1000, data_16, 'Q18')
```

```{r}
#res <- NA
#for (i in 1:10) {
#    res[i] <- data_16[ , .(group_mean = mean(Q18)), keyby = .(sample('FL_24_DO'))][ , diff('FL_24_DO')]
#}
#dist_sharp_null <- res
#hist(dist_sharp_null)
#abline(v=ate, lwd=3, col='blue')
```

```{r}
num_larger <- sum(ate_result >= ate_18)
p_value_one_tailed <- num_larger/length(ate_result)
p_value_one_tailed
```

```{r}
p_value_two_tailed <- sum(abs(ate_result) >= abs(ate_18))/1000
p_value_two_tailed
```

### Random Inference with Package
```{r}
table_18 <- data.frame(Y = as.numeric(data_16$Q18),
                        Z = as.numeric(data_16$FL_24_DO))
table_18$Z[table_18$Z=='DataVisualization(Treatment)'] <- 1
table_18$Z[table_18$Z=='DataVisualization(Control)'] <- 0
table_18 <- na.omit(table_18)
#random inference
declartion <- declare_ra(N=30, m=15)
ri2_out <- conduct_ri(
  formula= Y ~ Z,
  declaration = declartion,
  sharp_hypothesis = 0,
  data = table_18
)
summary(ri2_out)
```

## Data Analysis

### Seperate data for control and treatment
```{r}
control <- d %>% filter(FL_24_DO=='DataVisualization(Control)')
treatment <- d %>% filter(FL_24_DO=='DataVisualization(Treatment)')
control_16 <- control  %>% filter(startsWith(StartDate, '7/16/20'))
treatment_16 <- treatment  %>% filter(startsWith(StartDate, '7/16/20'))
mean(as.numeric(control_16$Q19))
sd(as.numeric(control_16$Q19))
mean(as.numeric(treatment_16$Q19))
sd(as.numeric(treatment_16$Q19))
#power.t.test(n=15,delta=0.3,sd=0.28,type="two.sample")
#cohensD(as.numeric(treatment_16$Q19), as.numeric(control_16$Q19))
```

### Extract veriable from raw data into a new dataframe 
```{r}
Q19_table_16_more_vars <- data.frame(Y = as.numeric(data_16$Q19),
                                    vis = as.numeric(data_16$FL_24_DO),
                                   sick = as.numeric(data_16$Q9),
                                   hospitalized = as.numeric(data_16$Q10),
                                   dead = as.numeric(data_16$Q11),
                                   male = as.numeric(data_16$Q4),
                                   age = as.numeric(data_16$Q5),
                                   ethinicity = as.numeric(data_16$Q6),
                                   political = as.numeric(data_16$Q7),
                                   education = as.numeric(data_16$Q8))

Q18_table_16_more_vars <- data.frame(Y = as.numeric(data_16$Q18),
                                    vis = as.numeric(data_16$FL_24_DO),
                                   sick = as.numeric(data_16$Q9),
                                   hospitalized = as.numeric(data_16$Q10),
                                   dead = as.numeric(data_16$Q11),
                                   male = as.numeric(data_16$Q4),
                                   age = as.numeric(data_16$Q5),
                                   ethinicity = as.numeric(data_16$Q6),
                                   political = as.numeric(data_16$Q7),
                                   education = as.numeric(data_16$Q8))
```


### Check Variable Correlation and Covariate Balance
```{r}
chart.Correlation(Q19_table_16_more_vars, histogram=TRUE)
```

```{r}
chart.Correlation(Q18_table_16_more_vars, histogram=TRUE)
```

#### Check Time
```{r}
control_16_duration <- as.numeric(control_16$`Duration (in seconds)`)

treatment_16_duration <- as.numeric(treatment_16$`Duration (in seconds)`)

par(mfrow=c(1,2))
hist(control_16_duration, col=rgb(0,0,1,0.5))
hist(treatment_16_duration, col=rgb(0,0,1,0.5))
mean(control_16_duration)
mean(treatment_16_duration)
```


#### Check Variable Interval
```{r}
control <- Q18_table_16_more_vars %>% filter(vis==0)
treatment <- Q18_table_16_more_vars %>% filter(vis==1)
cat("           control      treatment \n")
cat("gender        ",IQR(control$gender), "        ", IQR(treatment$gender), "\n")
cat("age           ",IQR(control$age), "       ", IQR(treatment$age), "\n")
#cat("ethinicity    ",IQR(control$ethinicity), "          ", IQR(treatment$ethinicity), "\n")
cat("political     ",IQR(control$political), "       ", IQR(treatment$political), "\n")
cat("education     ",IQR(control$education), "       ", IQR(treatment$education), "\n")
cat("sick          ",IQR(control$sick), "       ", IQR(treatment$sick), "\n")
cat("hospitalized  ",IQR(control$hospitalized), "          ", IQR(treatment$hospitalized), "\n")
cat("dead          ",IQR(control$dead), "          ", IQR(treatment$dead), "\n")
```


#### Visualization
```{r}
concern_control <- as.numeric(control_16$Q18)
concern_treatment <- as.numeric(treatment_16$Q18)
mean(concern_control)
mean(concern_treatment)
concern_ate <- mean(concern_treatment) - mean(concern_control)
par(mfrow=c(1,2))

hist(concern_control, col=rgb(1,0,0,0.5), xlim=c(0,7), ylim=c(0,10))
hist(concern_treatment, col=rgb(0,0,1,0.5), xlim=c(0,7), ylim=c(0,10))
mtext("How concerned are you about the spread of COVID-19 virus in the US?", side=1, outer=TRUE, line=-1)

```

```{r}
is_it_a_issue_control <- as.numeric(control_16$Q19)
is_it_a_issue_treatment <- as.numeric(treatment_16$Q19)
mean(is_it_a_issue_treatment) - mean(is_it_a_issue_control)
par(mfrow=c(1,2))


hist(is_it_a_issue_control, col=rgb(1,0,0,0.5), xlim=c(0,7), ylim=c(0,10))
hist(is_it_a_issue_treatment, col=rgb(0,0,1,0.5), xlim=c(0,7), ylim=c(0,10))
mtext("Which statement is closest to your viewpoint on COVID-19 deaths in the US?	", side=1, outer=TRUE, line=-1)
```

```{r}
trust_control <- as.numeric(control_16$Q17)
trust_treatment <- as.numeric(treatment_16$Q15)
mean(trust_treatment) - mean(trust_control)
par(mfrow=c(1,2))
par(mfrow=c(1,2))


hist(trust_control, col=rgb(1,0,0,0.5), xlim=c(0,3), ylim=c(0,30))
hist(trust_treatment, col=rgb(0,0,1,0.5), xlim=c(0,3), ylim=c(0,30))
mtext("I trust that the information presented in the data visualization is accurate", side=1, outer=TRUE, line=-1)
```


```{r}
q11_control <- as.numeric(control_16$Q11)
q11_treatment <- as.numeric(treatment_16$Q11)
mean(q11_treatment) - mean(q11_control)
par(mfrow=c(1,2))


hist(q11_control, col=rgb(1,0,0,0.5), xlim=c(0,3), ylim=c(0,30))
hist(q11_treatment, col=rgb(0,0,1,0.5), xlim=c(0,3), ylim=c(0,30))
mtext("Has anyone you know died from COVID-19?	", side=1, outer=TRUE, line=-1)
```

```{r}

q10_control <- as.numeric(control_16$Q10)
q10_treatment <- as.numeric(treatment_16$Q10)
mean(q10_treatment) - mean(q10_control)
par(mfrow=c(1,2))


hist(q10_control, col=rgb(1,0,0,0.5), xlim=c(0,3), ylim=c(0,30))
hist(q10_treatment, col=rgb(0,0,1,0.5), xlim=c(0,3), ylim=c(0,30))
mtext("Has anyone you know died from COVID-19?	", side=1, outer=TRUE, line=-1)

```

```{r}

q9_control <- as.numeric(control_16$Q9)
q9_treatment <- as.numeric(treatment_16$Q9)
mean(q9_treatment) - mean(q9_control)
par(mfrow=c(1,2))


hist(q9_control, col=rgb(1,0,0,0.5), xlim=c(0,3), ylim=c(0,30))
hist(q9_treatment, col=rgb(0,0,1,0.5), xlim=c(0,3), ylim=c(0,30))
mtext("Has anyone you know died from COVID-19?	", side=1, outer=TRUE, line=-1)
```


### Encode data to dummy indicator
```{r}
Q19_table_16_more_vars$asian[Q19_table_16_more_vars$ethinicity=='1'] <- 1
Q19_table_16_more_vars$asian[Q19_table_16_more_vars$ethinicity!='1'] <- 0
Q19_table_16_more_vars$africaamerica[Q19_table_16_more_vars$ethinicity=='2'] <- 1
Q19_table_16_more_vars$africaamerica[Q19_table_16_more_vars$ethinicity!='2'] <- 0
Q19_table_16_more_vars$caucasian[Q19_table_16_more_vars$ethinicity=='3'] <- 1
Q19_table_16_more_vars$caucasian[Q19_table_16_more_vars$ethinicity!='3'] <- 0
Q19_table_16_more_vars$latino[Q19_table_16_more_vars$ethinicity=='4'] <- 1
Q19_table_16_more_vars$latino[Q19_table_16_more_vars$ethinicity!='4'] <- 0
Q19_table_16_more_vars$india[Q19_table_16_more_vars$ethinicity=='5'] <- 1
Q19_table_16_more_vars$india[Q19_table_16_more_vars$ethinicity!='5'] <- 0

Q19_table_16_more_vars$repulican[Q19_table_16_more_vars$political=='1'] <- 1
Q19_table_16_more_vars$repulican[Q19_table_16_more_vars$political!='1'] <- 0
Q19_table_16_more_vars$democrat[Q19_table_16_more_vars$political=='2'] <- 1
Q19_table_16_more_vars$democrat[Q19_table_16_more_vars$political!='2'] <- 0
Q19_table_16_more_vars$indepedent[Q19_table_16_more_vars$political=='3'] <- 1
Q19_table_16_more_vars$indepedent[Q19_table_16_more_vars$political!='3'] <- 0
Q19_table_16_more_vars$sthelse[Q19_table_16_more_vars$political=='4'] <- 1
Q19_table_16_more_vars$sthelse[Q19_table_16_more_vars$political!='4'] <- 0
Q19_table_16_more_vars <- na.omit(Q19_table_16_more_vars)
```

```{r}
Q18_table_16_more_vars$asian[Q18_table_16_more_vars$ethinicity=='1'] <- 1
Q18_table_16_more_vars$asian[Q18_table_16_more_vars$ethinicity!='1'] <- 0
Q18_table_16_more_vars$africaamerica[Q18_table_16_more_vars$ethinicity=='2'] <- 1
Q18_table_16_more_vars$africaamerica[Q18_table_16_more_vars$ethinicity!='2'] <- 0
Q18_table_16_more_vars$caucasian[Q18_table_16_more_vars$ethinicity=='3'] <- 1
Q18_table_16_more_vars$caucasian[Q18_table_16_more_vars$ethinicity!='3'] <- 0
Q18_table_16_more_vars$latino[Q18_table_16_more_vars$ethinicity=='4'] <- 1
Q18_table_16_more_vars$latino[Q18_table_16_more_vars$ethinicity!='4'] <- 0
Q18_table_16_more_vars$india[Q18_table_16_more_vars$ethinicity=='5'] <- 1
Q18_table_16_more_vars$india[Q18_table_16_more_vars$ethinicity!='5'] <- 0

Q18_table_16_more_vars$repulican[Q18_table_16_more_vars$political=='1'] <- 1
Q18_table_16_more_vars$repulican[Q18_table_16_more_vars$political!='1'] <- 0
Q18_table_16_more_vars$democrat[Q18_table_16_more_vars$political=='2'] <- 1
Q18_table_16_more_vars$democrat[Q18_table_16_more_vars$political!='2'] <- 0
Q18_table_16_more_vars$indepedent[Q18_table_16_more_vars$political=='3'] <- 1
Q18_table_16_more_vars$indepedent[Q18_table_16_more_vars$political!='3'] <- 0
Q18_table_16_more_vars$sthelse[Q18_table_16_more_vars$political=='4'] <- 1
Q18_table_16_more_vars$sthelse[Q18_table_16_more_vars$political!='4'] <- 0
Q18_table_16_more_vars <- na.omit(Q18_table_16_more_vars)
```

### Model
```{r}
m1 <- lm(Y ~ vis + sick + hospitalized  + vis*sick + vis*hospitalized, data = table_16_more_vars)
m2 <- lm(Y ~ vis + sick + hospitalized  + vis*sick + vis*hospitalized + repulican + democrat  + repulican*vis + democrat*vis , data = table_16_more_vars)
m3 <- lm(Y ~ vis + sick + hospitalized + repulican + democrat + repulican*vis + democrat*vis  + vis*sick + vis*hospitalized + + male + male*vis , data = table_16_more_vars)
confint(m1, 'vis', level=0.95)
stargazer(
    m1,m2,m3, 
    type = 'text',
    header=F
  )
```


```{r}
#robust_se_2 <- sqrt(diag(vcovHC(mod_2)))
```

```{r}
#stargazer(mod_2, se = list(robust_se_2) , type = 'text')
```
